%1st paragraph
%1
\revised{This paper proposes a system that classifies postures with hand movement of office workers, a remaining issue in prior work, using a light detection-and-ranging (LiDAR) sensor network.}
\deleted{This paper proposes an edge computing system for classifying postures with hand movement of office workers, which was left as a remaining issue in prior work, using a light detection-and-ranging (LiDAR) sensor network.}
%2
\revised{The LiDAR sensor network acquires human poses with hand movement; preprocessing includes trimming, calibration, feature estimation, clustering, and normalization before deep-learning classification.}
\deleted{The proposed system utilizes the LiDAR sensor network to acquire human poses with hand movement and performs preprocessing steps including trimming, calibration, feature estimation, clustering, and normalization.}
%3
\deleted{It then classifies the postures by using deep learning.}

%2nd paragraph
%4
\revised{Experiments capture posture data from multiple subjects using multiple LiDAR sensors and vary point features and clustering methods.}
%5
\revised{Classification accuracy is reported to compare preprocessing configurations.}
\deleted{To experimentally evaluate the proposed system, we capture and store human posture data using multiple LiDAR sensors on various individuals and perform preprocessing before the classification.}
%6
\deleted{We explore several different conditions, i.e., data type, LiDAR placement, features, and clustering methods, trained the models, and then evaluate the trained models based on classification accuracy and confusion matrices.}
%7
\revised{The results show effective classification under various preprocessing configurations.}
\deleted{The results demonstrate how the proposed system works with various sets of preprocessing methods.}
