%1st paragraph
%1
Table~\ref{accresults} shows the accuracy for all twelve combinations of features and clustering methods used.
%2
\revised{Subjects A to AB served as the test dataset for four posture classes.}
\revised{Four posture classes yield a 25\% baseline accuracy under uniform random guessing.}
\revised{Accuracy exceeded the 25\% baseline in all cases in Table~\ref{accresults}.}
%3
\revised{Depending on the feature and clustering combination, test accuracy was stable or varied across test subjects in Table~\ref{accresults}.}
\deleted{Classification accuracy varied across test subjects because point-cloud density and body size differed from the three training subjects.}
\begin{deletedblock}
The accuracy is reported with the data from subjects A to AB serving as the test dataset.
Since we are classifying 4 posture classes, a baseline accuracy of 25\% or higher is expected. 
In all cases Table~\ref{accresults}, the accuracy exceeded the baseline.
\end{deletedblock}

%2nd paragraph
%4
Regarding the clustering methods, no clustering or DBSCAN tended to achieve higher accuracy than K-means.
  %4-1
  \revised{k-means tended to achieve lower accuracy than no clustering or DBSCAN for the same feature type.}
  \deleted{k-means tended to lower accuracy by removing hand-region points required to distinguish typing from pad operation.}

%3rd paragraph
%5
In terms of features, normals tended to yield higher accuracy when no clustering or DBSCAN was employed.
  %5-1
  \revised{Classification using normals yielded comparatively stable test accuracy in Table~\ref{accresults}.}
  \deleted{Normals yielded stable test accuracy when no clustering or DBSCAN was applied.}
  %5-2
  \revised{Dimensionality features resulted in higher accuracies than the other three feature types for several test subjects outside the training set of subjects A, B, and C in Table~\ref{accresults}.}
  \deleted{Dimensionality features achieved higher accuracy than other features for several subjects outside the training set when local shape resembled training examples.}

\input{tex/evaluation/accuracy/table.tex}
