%分類モデルごとの各表の説明
%|-テストデータごとの表の説明
% |-表から読み取れること
% |-考察

% \noindent{\red{Todo:左LiDARの6組について、テストデータからStayをなしにした3分類での精度表とマトリクスを示し、精度が上がる/下がるかを考察する。}}\\

% NOTE:
% - Tables are generated into tex/evaluation/confusion-matrices/table.tex

% Confusion matrices (text only; tables are in confusion-matrices-tables.tex)

Tables~\ref{normalnonematrix} and \ref{normalkmeansmatrix} present \deleted{confusion matrices for each subject} \revised{representative confusion matrices for test subjects A to AB}.
%
The rows represent the ground truth labels, and the columns represent the inferred labels.
%
\deleted{Table~\ref{normalnonematrix} and Table~\ref{normalkmeansmatrix} correspond to the results shown in Table~\ref{accresults}(a) and Table~\ref{accresults}(i), respectively.}
%
\begin{revisedblock}
We compare two conditions to examine the effect of clustering.
  %
  The conditions are: normals without clustering and normals with k-means.
\end{revisedblock}
%
\deleted{Both of these used normals as features; however, Table~\ref{accresults}(a) exhibited high accuracy, while Table~\ref{accresults}(i) showed lower accuracy.}
\revised{Both of the used normals as features; however, the normals without clustering tended to show higher accuracy, while the normals with k-means tended to show lower accuracy in Table~\ref{accresults}.}
%
In Table~\ref{normalnonematrix}, the diagonal elements from the top-left to the bottom-right are large, indicating that the inferred labels largely agreed with the ground truth. 
%
However, there were frequent misclassifications of typing as pad operation. 
%
This is likely due to the difficulty in distinguishing whether both hands were touching the pad or the keyboard. 
%
In Table~\ref{normalkmeansmatrix}, in addition to misclassifying typing as pad operation, there were also frequent misclassifications of pad operation as typing.
  
  
% NOTE: subfig's default (a)...(z) overflows for 28 subfloats in a table
% (uses the `subtable` counter). Use numeric labels locally.
{
\renewcommand{\thesubtable}{\arabic{subtable}}
\input{tex/evaluation/confusion-matrices/table.tex}
}