\subsection{Model architecture}
\label{sec:model}
\begin{deletedblock}
\input{tex/related-works/model-architecture.tex}
\end{deletedblock}

%1st paragraph
%1.
\revised{Classification associates each data sample with the category of highest estimated probability.}
%2.
\revised{Deep learning models for point cloud classification have attracted interest \cite{grandini2020metrics}.}
%3.
\revised{Early approaches relied on voxelization \cite{Wu_2015_CVPR,7353481,Qi_2016_CVPR}.}
%4.
\revised{Qi et al. presented PointNet, which applies shared multilayer perceptrons (MLPs) to each point and aggregates features with max pooling under permutation invariance \cite{grandini2020metrics}.}
%5.
\revised{Subsequent models such as PointCNN \cite{NEURIPS2018_f5f8590c}, ShellNet \cite{Zhang_2019_ICCV}, A-CNN \cite{Komarichev_2019_CVPR}, SO-Net \cite{Li_2018_CVPR}, and Kd-network \cite{8237361} learn hierarchical local structure from point coordinates.}
%6.
\revised{The existing research comprises direct classification architectures and spatial modeling using local relationships.}
%7.
\revised{The present study targets fine-grained hand-movement classification in a multi-person office environment, unlike macro-posture or static object classification.}

\subsection{Improvement for object detection}
\label{sec:improvement}
\begin{deletedblock}
\input{tex/related-works/improvement-for-object-detection.tex}
\end{deletedblock}

%1st paragraph
%1.
\revised{Point features encode inter-point relationships and local shape and are used with point coordinates as machine-learning inputs.}
%2.
\revised{Eigenvalue-based features from neighborhood covariance matrices include entropy and omnivariance \cite{rs9030277, 9132746, 8490990}.}
%3.
\revised{Convex-hull descriptors \cite{9353594} and higher-dimensional descriptors such as signature of histograms of orientations (SHOT) \cite{SALTI2014251} and position and orientation distribution (POD) \cite{10.1145/2671188.2749380} capture object shape for recognition and retrieval.}
%4.
\revised{The present study applies point feature preprocessing to hand-movement classification in a multi-person office environment.}
