%点群を分類するディープラーニングの関連研究

\begin{deletedblock}
%1st paragraph
%1分類について
Classification estimates which category a given data sample belongs to. 
  %1-1
  Probabilities that a given data sample belongs to each category are estimated and the data is then associated with the category with the highest probability. 
  %1-2
  Machine learning is widely utilized for such estimation, and recently, classification from point cloud data using deep learning models has been attracting interest \cite{grandini2020metrics}.
  % Machine learning is widely utilized for such estimation \cite{grandini2020metrics}, and recently, classification from point cloud data has been studied. 
  %1-3
  The difference of our study from the related works introduced below is that we address an edge system that captures detailed movements of hands using multiple LiDAR sensors. 
%2
% Recently, classification from point cloud data using deep learning models has been attracting interest. 
  %2-1
  % As machine learning models for point cloud data, deep learning models for point cloud data have attracted attention from researchers.
\end{deletedblock}

\begin{revisedblock}
%1st paragraph
%1 分類の説明
Classification estimates which category a given data sample belongs to by associating it with the highest estimated probability.
%2 深層学習による点群分類の潮流
Deep learning models for point cloud classification have attracted interest \cite{grandini2020metrics}.

% %2nd paragraph
% %1
% While early models used voxelization \cite{Wu_2015_CVPR,7353481,Qi_2016_CVPR}, Qi et al. presented PointNet, which directly processes point clouds by considering permutation invariance \cite{grandini2020metrics}.
% %2
% PointCNN addresses convolution challenges on point clouds using the X-Conv operator to weight and permute input features \cite{NEURIPS2018_f5f8590c}.
% %3
% ShellNet extracts features from concentric shells to maintain local structures \cite{Zhang_2019_ICCV}, and A-CNN utilizes annular convolutions for hierarchical feature processing \cite{Komarichev_2019_CVPR}.
% %4
% SO-Net models spatial distributions via self-organizing maps (SOM) \cite{Li_2018_CVPR}, while Kd-network employs tree-based partitions for classification without grid reliance \cite{8237361}.
\end{revisedblock}

\begin{deletedblock}
%2nd paragraph
%1PointNet以前の点群の分類
Although there are some models that process voxelization, until recently there have been no models that directly process point clouds \cite{Wu_2015_CVPR,7353481,Qi_2016_CVPR}.
%2PointNet
Qi et al. presented a network called PointNet, which is a deep learning model capable of directly classifying point clouds. 
    %2-1
    Machine learning for such estimation has been widely used \cite{grandini2020metrics}. 
    %2-2
    PointNet transforms the point clouds, uses a multilayer perceptron (MLP) to process the transformed point clouds, and then implements max pooling to process the features that are extracted by the MLP. 
    %2-3
    PointNet can process point clouds directly by considering the permutation invariance of the input points. 
\end{deletedblock}

\begin{revisedblock}
%2nd paragraph
%1PointNet以前の点群の分類
Early approaches relied on voxelization \cite{Wu_2015_CVPR,7353481,Qi_2016_CVPR}.
%2PointNet
Qi et al. presented PointNet \cite{grandini2020metrics}.
    %2-1深層学習モデルとしての位置づけ
    The network is a deep learning model for point cloud classification.
    %2-2共有MLPによる点ごとの特徴抽出
    PointNet applies shared multilayer perceptrons (MLPs) to each point in a set.
    %2-3max poolingによる特徴集約
    The model aggregates per-point features using max pooling.
    %2-4置換不変性
    The architecture enforces permutation invariance over the input order.
\end{revisedblock}

\begin{deletedblock}
%3rd paragraph
%1CNNを使った点群の分類
Point cloud-based classification models are typically based on deep learning using convolutional neural networks (CNNs). 
  %1-1PointCNN
  Li et al. presented PointCNN, which addresses the challenges of convolution on point clouds by implementing an efficient end-to-end permutation-invariant convolution for point cloud deep learning \cite{NEURIPS2018_f5f8590c}.
    %1-1-1
    This method uses point cloud coordinates and point features as input data and implements a technique called X-Conv to process the input data hierarchically. 
      %1-1-1-1
      X-Conv moves the point cloud from the input data and uses a MLP to process the moved point clouds. 
      %1-1-1-2
      It then concatenates the processed point clouds with the point features from the input data and generates an X-transformation matrix from the point clouds processed using a MLP by utilizing the concatenated features and the X-transform matrix to weight and permute, respectively. 
      %1-1-1-3
      Finally, it processes the weighted features using typical convolution. 
  %1-2ShellNet
  Zhang et al. presented a model called ShellNet that performs classification while converting point clouds and extracting features from the relationships between points and their neighbors using CNN \cite{Zhang_2019_ICCV}. 
    %1-2-1
    This model utilizes point cloud coordinates as input data and implements a technique called ShellConv to process the input data hierarchically. 
      %1-2-1-1
      ShellConv selects a few points from the entire point cloud and creates a point set consisting of adjacent points centered around the selected points. 
      %1-2-1-2
      It then transforms the coordinates of each point using the center of the point set as the origin. 
      %1-2-1-3
      It utilizes a multilayer perceptron (MLP) to process the transformed point clouds and concatenates the processed point cloud with the point features from a previous level. 
      %1-2-1-4
      It then separates each point set into multiple shells and performs max pooling on the points within each shell. 
      %1-2-1-5
      Finally, it concatenates the features from all shells and performs convolution. 
  %1-3A-CNN
  Komarichev et al. presented a method called A-CNN as a classification model using CNN \cite{Komarichev_2019_CVPR}. 
    %1-3-1
    A-CNN is a type of machine learning model that directly convolutes a 3D point cloud. 
    %1-3-2
    It takes the normals and coordinates of point cloud data as input data and then implements farthest point sampling and a technique called annular convolutions to process the input data hierarchically. 
      %1-3-2-1
      Annular convolutions uses k-nearest neighbor search to create a group of adjacent points around each point selected in the FPS. 
      %1-3-2-2
      It sets a plane on each group based on the normal of the center point, and rearranges the points within the plane. 
      %1-3-2-3
      It then performs a convolution on each point group. 
      %1-3-2-4
      Finally, it performs max pooling on the features from the convolution.
\end{deletedblock}

\begin{revisedblock}
%3rd paragraph
%1CNNを使った点群の分類
Point cloud classifiers often adopt convolutional neural networks (CNNs).
  %1-1PointCNN
  Li et al. presented PointCNN \cite{NEURIPS2018_f5f8590c}.
    %1-1-1X-Convの導入
    The method introduces X-Conv for point cloud deep learning.
    %1-1-2置換不変畳み込み
    The operator performs end-to-end permutation-invariant convolution.
    %1-1-3座標からの階層的局所特徴学習
    The architecture learns hierarchical local features from point coordinates.
    %1-1-4点属性の利用
    The architecture uses point attributes as additional inputs.
  %1-2ShellNet
  Zhang et al. presented ShellNet \cite{Zhang_2019_ICCV}.
    %1-2-1ShellConvによる近傍特徴集約
    The model aggregates neighborhood features using ShellConv.
    %1-2-2同心円シェル分割
    The operator partitions local point sets into concentric shells.
    %1-2-3局所構造の保持
    The network extracts hierarchical features to preserve local structures.
  %1-3A-CNN
  Komarichev et al. presented A-CNN \cite{Komarichev_2019_CVPR}.
    %1-3-1環状畳み込み
    The method applies annular convolutions on a three-dimensional (3D) point cloud.
    %1-3-2最遠点サンプリング
    The pipeline uses farthest point sampling (FPS) to select center points.
    %1-3-3法線入力
    The model takes point normals as inputs.
    %1-3-4座標入力
    The model takes point coordinates as inputs.
    %1-3-5近傍からの階層的特徴学習
    The network learns hierarchical features from sampled neighborhoods.
\end{revisedblock}

\begin{deletedblock}
%3rd paragraph
%1点群の分類におけるその他のアプローチ
While there are several machine learning models that process point clouds directly, other approaches are attracting interest as well. 
  %1-1SO-Net
  Li et al. proposed a method called SO-Net, a non-point cloud based approach that encodes point clouds into a one-dimensional array and processes the array through a multilayer perceptron (MLP) \cite{Li_2018_CVPR}. 
    %1-1-1
    SO-Net utilizes the coordinates of point cloud data as input data and models a spatial distribution of the point clouds by constructing a self-organizing map (SOM) \cite{58325}. 
    %1-1-2
    SO-Net represents the input point cloud with a single feature vector and operates while systematically adjusting the overlap of receptive fields by searching for the k-nearest neighbor algorithm between nodes on the SOM. 
    %1-1-3
    It then normalizes the features from the k-nearest neighbor algorithm and processes the normalized features through fully connected layers with a k-nearest neighbor algorithm using max pooling. 
    %1-1-7
    % SO-Net processes the normalized features through fully connected layers. 
    %1-1-8
    % SO-Net processes the features from the fully connected layers with a k-nearest neighbor algorithm. 
    %1-1-9
    % SO-Net processes features from the k-nearest neighbor algorithm using max pooling. 
  %1-2Kd-Network
  Klokov et al. proposed a deep learning architecture called Kd-network that transforms point clouds and then performs machine learning \cite{8237361}. 
    %1-2-1
    Kd-network utilizes Kd-tree to obtain features and pass them through an MLP to classify objects. 
    %1-2-2
    It uses point coordinates as input data and constructs a kd-tree to partition each point cloud. 
    %1-2-3
    Finally, it performs affine transformation on the pairwise vectors of two adjacent nodes for each node. 
    %1-2-4
    Unlike convolutional architectures that require rasterization on a uniform two-dimensional or three-dimensional grid, which is currently mainstream, Kd-network does not rely on a grid at all. 
\end{deletedblock}

\begin{revisedblock}
%4th paragraph
%1点群の分類におけるその他のアプローチ
  %1-1SO-Net
  Li et al. proposed SO-Net \cite{Li_2018_CVPR}.
    %1-1-1固定長符号化
    The method encodes a point cloud into a fixed-length representation.
    %1-1-2SOMによる空間分布モデル化
    The encoder builds a self-organizing map (SOM) over point coordinates \cite{58325}.
    %1-1-3k-NNによる特徴洗練
    The pipeline refines features using k-nearest neighbor (k-NN) search.
    %1-1-4max pooling
    The network applies max pooling over the refined features.
  %1-2Kd-Network
  Klokov et al. proposed Kd-network \cite{8237361}.
    %1-2-1kd-tree構築
    The architecture constructs a kd-tree over point coordinates.
    %1-2-2ノード間ベクトルへのアフィン変換
    The model applies affine transforms on inter-node vectors along the tree.
    %1-2-3MLPによる分類
    The pipeline passes the resulting features through an MLP for classification.
    %1-2-4グリッド非依存の分類
    The method classifies objects without rasterizing points onto a uniform grid.

% \end{spverbatim}
%5th paragraph
%1 既存研究の特徴
The existing research shown above can be broadly classified into the following two categories:
\begin{enumerate}
  %1-1直接分類アーキテクチャ
  \item Architectures for direct point cloud classification (e.g., PointNet, PointCNN).
  %1-2局所関係の空間モデリング
  \item Spatial modeling techniques using local relationships (e.g., ShellNet, SO-Net, A-CNN, Kd-network).
\end{enumerate}
%2 本研究の特徴
Our research targets the fine-grained classification of hand movements in a multi-person office environment.
%3 本研究との差分 
Our research differs from the macro-posture or static object classification focused on in the categories above.
  % %3-1 本研究との差分
  % The study additionally proposes an edge system for capturing detailed hand movements using a LiDAR sensor network.
\end{revisedblock}