% \begin{spverbatim}
%1st paragraph
%1
\revised{An experimental system was built from the model in Fig.~\ref{system}.}
\deleted{We developed an experimental system based on the proposed system shown in Fig.~\ref{system}.}
%2
The experimental system consisted of two sets of LiDAR units (Mid-70 units), two edge devices (Jetson nano units), an edge computer (Jetson Xavier NX and Jetson Orin nano), and a regular keyboard \cite{Mid70,Jetsonnano,JetsonNX,Jetsonorinnano}.
  %2-1
  \revised{The experiment was conducted at 14Q32, 14F, Shibaura Institute of Technology, Toyosu, Koto-ku, Tokyo.}
  %2-2
  \revised{Two Livox Mid-70 LiDAR units were deployed at a sensor frame rate of 10 fps.}
  %2-3
  \revised{Two NVIDIA Jetson nano edge devices were used.}
  %2-4
  \revised{An NVIDIA Jetson Xavier NX edge computer was used for training data and test data A, B, and C acquisition.}
  %2-5
  \revised{An NVIDIA Jetson Orin nano edge computer was used for test data A to AB acquisition.}
\deleted{Table~\ref{experiment} lists the specifications of the experiment.}

%2nd paragraph
%3
\revised{Training data and test data A, B, and C were acquired on 9 December 2022.}
%4
\revised{Test data A to AB were acquired on 12 December 2024.}
%5
\revised{3 contributors provided training data.}
%6
\revised{28 contributors provided test data.}

\begin{deletedblock}
\begin{table}[b]
	\caption{Specifications of experiment.}
	\label{experiment}
    \scalebox{0.9}{
	\begin{tabular}{l|l}
        \hline
        Parameter & Value \\ \hline
        Place & 14Q32, 14F, Shibaura Institute \\
        &of Technology, Toyosu, Koto-ku, \\ 
        &Tokyo \\
        Date of training data \\
        and test data A, B, \\
        and C acquisition & 9 December 2022 \\
        Date of test data \\
        A to AB acquisition & 12 December 2024 \\
        LiDAR units & Livox Mid-70 \\
        No. of LiDAR units & 2 \\
        Edge devices & NVIDIA Jetson nano \\
        No. of edge devices & 2 \\
        Edge computer for training data \\ 
        and test data A, B, \\
        and C acquisition & NVIDIA Jetson Xavier NX \\
        Edge computer for test data \\ 
        A to AB acquisition & NVIDIA Jetson Orin nano \\
        Frame rate of sensor & 10 fps \\
        No. of contributors for training data & 3 \\
        No. of contributors for test data & 28 \\
        \hline
 \end{tabular}
 }
\end{table}
\end{deletedblock}
% \end{spverbatim}
