% \noindent{\red{Todo:分類時のキャリブレーションについて述べる。}}\\

% \noindent{\red{1段落目:提案システムの処理をSection.~\ref{sec:method}に示された方法論に基づいて行っていることを述べる。}}

% \noindent{\red{2段落目:キャリブレーション、トリミング、特徴付与の具体的な方法を述べる。ここでは特徴付与時のパラメータについて述べる。}}

% \noindent{\red{3段落目:使用したPointnet++のリポジトリ、分類時の統一するテータ内の点の数、クラスタリングのパラメータを述べる。}}

% \noindent{\red{\sout{4}3段落目:クラスタリングのパラメータについて述べている。ここは3章とまとめる。4段落までsemiの内容。}}
%sec:j
%
% \noindent{\red{4段落目:学習データと検証データの分け方について述べている。そこから、分類モデルを生成することも述べる。}}

% \begin{spverbatim}
%1Methodologyに基づいた処理
% In the experiment, processing of the proposed system was performed following the methodology presented in Section~\ref{sec:method}. 
In our experiment, the proposed system was processed according to the methodology described in Section~\ref{sec:method}. 

  %1-1トリミング
  Two vertices of the region where a person is located were determined and then the point clouds were trimmed. 
  
%   For the calibration, we used RANSAC and ICP based on the method \cite{GlobalRegistration} from Open3D \cite{zhou2018open3d}, which is a common library for processing point clouds. 

  %1-2特徴抽出
  The features were generated using the process explained in Section~\ref{sec:method}. 
    %1-2-1法線
    Specifically, the normal estimator from Open3D was used and normals were stored with the coordinate data in point cloud data files. 
    %1-2-2Dimensionality featureとProportion of variance
    The covariances were generated and then the dimensionality features and the proportion of variance were calculated. 
    %1-2-3FPFH
    The FPFH estimator from Open3D was utilized and the FPFH values were stored in a separate file from the coordinate data. 

  %1-3クラスタリング
  The data were clustered using the process explained in Section~\ref{sec:method}. 
    %1-3-1DBSCAN
    Specifically, outliers and some clusters were removed after implementing DBSCAN.
    %1-3-2k-means
    Some clusters were also removed after performing k-means. 

  %1-4ダウンサンプリング
  After the clustering and downsampling, the number of points in each point cloud was adjusted to 4,096, which is the default value of the Github repository \cite{pytorchpointnet++}. 

  %1-5正規化
  Normalization was performed using different values for each point cloud dataset used for the training. 
  %  For each point cloud dataset used for the evaluation, we normalized using the same value. 

  %1-6Data augmentation
  Data augmentation was performed on the normalized data. 
    %1-6-1PointCutMixについて
    For data augmentation, PointCutmix was used\cite{ZHANG202258}. 
        %1-6-1-1トレーニングデータの用意
        Three point clouds A, B, and C were prepared. 
        %1-6-1-2ベータ関数による値の設定
        The beta function was used to randomly determine a real number $\lambda$. 
        %1-6-1-3トレーニングデータAとBの処理
        Points from point cloud B were assigned to each point in point cloud A. 
            %1-6-1-3-1 2つの点群の各点の距離を計測し、一番近い点で置き換える
            For each point in A, the distance to all points in B was measured and the index of the closest point in B was assigned. 
            % \blue{We assigned the index of the point in the point cloud B that is closest to the point in the point cloud A to the point in the point cloud A. }
            % \blue{We repeated the following process for each point in the point cloud A. }
            %1-6-1-3-2上位λ%の点を置き換える
            Then, the top $\lambda$\% of points in A, sorted by distance, were replaced with their assigned points from B. 
        %1-6-1-4処理済みのAとCで処理
        Points from point cloud C were assigned to each point in point cloud A. 
            %1-6-1-4-1
            For each point in A, the distance to all points in B was measured and the index of the closest point in C was assigned. 
            % \blue{We assigned the index of the point in the point cloud C that is closest to the point in the point cloud A to the point in the point cloud A. }
            % \blue{We repeated the following process for each point in the point cloud A. }
            %1-6-1-4-2
            Then, the top $\lambda$\% of points in A, sorted by distance, were replaced with their assigned points from C. 
%
% \blue{We assigned points in the point cloud C to each point in the processed point cloud A as we does at the training data A and the training data B. }
% %1-3-1-3
% We assigned points in the point cloud C to each point in the point cloud A.
% %1-3-1-3-1
% We measured the distance from a coordinate of a point in the point cloud A to the coordinates of each point in the point cloud C.
% %1-3-1-3-2
% We assigned the index of the point in the point cloud C that is closest to the point in the point cloud A to the point in the point cloud A.
% %1-3-1-3-3
% We repeated the following process for each point in the point cloud A.
% %1-3-1-6
% In order of the distance between point cloud A and the selected point, replace the top λ\% of points with the point in point cloud C that has been assigned to that point.

  %1-7トレーニングデータは、学習用と研修用で4:1に分ける
  The remaining data were split into 4:1 for the training and validation. 
  %1-8PointNet++のグルーピングはMSGを使用
  Multi-scale grouping (MSG) was used to create groups in PointNet++, as based on prior methods \cite{pytorchpointnet++,PytorchPointnetPointnet2}.
  %1-9分類の出力
  An output containing the parameters of the classification was created after the training was completed. 
% \end{spverbatim}